Simple code showing off a couple of functions

Download Git.
Set configurations with
git config --global user.email "email@gmail.com"
git config --global user.name "username"

Open R.
File>New Project?Version Controlled> GIT

Create repository in github if you do not already have one.
Paste repository URL into where GIT request it. 

Write your code. Whenever you want to save, version control, and SHARE follow these steps
1. Save code
2. Git tab (next to environment and history) > select boxes > commit > in new window write a commit message > hit commit > hit push. 

Check github page to see it worked!


Duplicated Function - Example ofuse that removes duplicates and adds to a new df
```{r}
carsNoDuplicateSpeeds <- cars[!duplicated(cars$speed),]
```


Merge function. - 
```{r}
carsToMerge <- cbind(carsNoDuplicateSpeeds, seq(1:length(carsNoDuplicateSpeeds$speed)))
carsToMerge <- carsToMerge[,c(1,3)]
cars <- cars

mergedcars <- merge(x = cars, y = carsToMerge, by = "speed", all = TRUE)
```

